\subsection{The website does not collect automatically any information, except for the information contained in cookies.}

\subsection{"Cookies" are computer data, in particular text files that are stored in the terminal equipment of the Service User and are intended for the use of the websites of the Service. Cookies typically contain the name of the website from which time store them on a terminal device and a unique number.}

\subsection{Subject who inserts on End Users Device cookies files and has access to them is the Service Operator - /companyname}

\subsection{Cookies are used to:}
\begin{itemize}
\item adapt web content to the Service User preferences and to optimize the use of websites; 
\item in particular, these files allow you to recognize the device's Service and properly display the web page tailored to their individual needs;
\item produce statistics that help to understand how the Service Users benefit from web pages, which allows improving their structure and content;
\item maintenance of the Service User sessions (after logging in), so the user does not have on every page of the Service re-enter login and password;
\end{itemize}

\subsection{In the Service are used in two basic types of cookies: "session" (session cookies) and "fixed" (persistent cookies). Cookies "Session" are temporary files that are stored in the terminal equipment of a user to log out time, leave the website or disable the software (web browser). "Permanent" cookies are stored in the terminal equipment of a user for the time specified in the parameters of cookies or until their removal by the user.}

\subsection{In the Service are used in the following types of cookies:}
	\begin{itemize}
		\item "Essential" cookies, enabling the use of the services available within the Service, for example. Authentication cookies used for services that require authentication through the Service;

		\item Cookies used to ensure safety, eg. used to detect fraud in the field of authentication through the Service;

		\item "Performance" cookies, allowing the collection of information about how to use the websites of the Service;

		\item "Functional" cookies, allowing "remember" selected by the user settings and personalization of user interface, eg. In terms of the language or region from which the user font size, appearance, website, etc .;
	\end{itemize}

\subsection{In many cases, the software used to browse the web (browser) by default allows storage of cookies in the terminal equipment of a user. Service users can make at any time to change settings for cookies. These settings can be changed in particular in such a way as to block the automatic handling of cookies in your web browser configuration or inform about them every time you enter in the device's Service. Detailed information on the possibilities and ways of handling cookies are available in the software settings (web browser).}

\subsection{Service Operator announces that the restriction of the use of cookies may affect some of the functionality available on the websites of the Service.}

\subsection{Cookies posted at the edge of the Service User and may be used also by cooperating with the operator of the Service advertisers and partners.}

\subsection{More information about Cookies are available at http://www.allaboutcookies.org or in the "Help" menu in the web browser.}
 
